\hspace{2cm}
\parbox{.8\textwidth}{
\setlength{\parindent}{6pt}
\chapter{Language Science Press catalog}
\large
Language Science Press publishes high quality, peer-reviewed open-access books in linguistics. 

All books are available for free in PDF format from our website. For libraries and interested readers, we also offer hardcover and softcover copies for competitive prices. To order, follow the links on the books' pages. 

This catalog contains the 15 books from 8 series which have appeared up to now. As of today there are 16 series and 130 expressions of interest to publish with us. Future catalogs will contain the new books as they become available. For forthcoming books, check out our website at \url{http://www.langsci-press.org/catalog}

The series appearing with Language Science Press are listed below. Series marked with * are included in this catalog.

\begin{itemize}
\item African Language Grammars and Dictionaries
\item Classics in Linguistics*
\item Computational Models of Language Evolution*
\item Conceptual Foundations of Language Science*
\item Contemporary African Linguistics
\item Em­pir­i­cal­ly Ori­ent­ed The­o­ret­i­cal Mor­phol­o­gy and Syn­tax*
\item Implemented Grammars
\item Language Variation
\item Monographs on Comparative Niger-Congo
\item Morphological Investigations
\item Studies in Caribbean Languages
\item Studies in Diversity Linguistics*
\item Studies in Laboratory Phonology*
\item Textbooks in Language Sciences*
\item Topics at the Grammar-Discourse Interface
\item Translation and Multilingual Natural Language Processing*
\end{itemize}

For further information, please visit \url{http://www.langsci-press.org} or contact Sebastian Nordhoff at sebastian.nordhoff@langsci-press.org.
}

