% Flowchart
% Author: Stefan Kottwitz
% https://www.packtpub.com/hardware-and-creative/latex-cookbook
\documentclass[border=20pt]{article}
\date{}
\usepackage{color}
% \usepackage[vmargin=3cm,width=15cm]{geometry}
\usepackage{tikz}
\usetikzlibrary{matrix,calc,shapes}
\tikzset{
  treenode/.style = {shape=rectangle, 
                     draw, anchor=center,
                     text width=5em, align=center,
                     top color=white, bottom color=blue!20,
                     inner sep=1ex},
  decision/.style = {treenode, diamond, inner sep=0pt},
  root/.style     = {treenode, font=\Large, bottom color=red!30},
  env/.style      = {treenode, font=\ttfamily\normalsize},
  finish/.style   = {draw,top color=white, bottom color=green!20, font=\sffamily\large},
  dummy/.style    = {draw,top color=white, rounded corners, bottom color=orange!20, font=\sffamily\large}
}
\newcommand{\yes}{edge node [above] {yes}}
\newcommand{\no}{edge  node [left]  {no}}
\newcommand{\links}[1]{edge  node [left]  {#1}}
\newcommand{\rechts}[1]{edge  node [right]  {#1}}
\newcommand{\oben}[1]{edge  node [above]  {#1}}
\newcommand{\unten}[1]{edge  node [below]  {#1}}

\title{Reviewing of edited volumes}
\begin{document} 
\maketitle
\section*{Introduction}

\pagestyle{empty}

The review process of edited volumes is more complex than the review
process of articles or books. The contributions to edited volumes are
heterogeneous with regard to the quality of research and writing. The
scientific merit of each contribution has to be assessed. Furthermore,
the value of the volume should be greater than the sum of its parts.
There should be an overarching theme tying the contributions together
which will make it worthwhile for the reader to have the whole
collection rather than only one article.

In the review process, it is important to distinguish the quality
assurance of the individual articles from the assurance of the quality
of the overarching volume. In this blogpost, I will detail several
options how this can be achieved without imposing unnecessary friction
or rounds of review.  Some terminological conventions: the quality
assurance of individual articles, I will call "assurance of scientific
merit"; the quality assurance of the edited volume as a whole,
"assurance of coherence". I will furthermore distinguish between the
authors of the individual contributions, the volume editor (VE) and the
series editor (SE), assuming that the book will appear in a series like
Studies in Diversity Linguistics.

The overall coherence of the volume depends on the content of the
papers. Even if one or several papers were not of particularly high
quality, this would not make the volume incoherent: there would simply
be certain aspects of the theme of the volume that would be covered, but
in a less than optimal way. This means that assurance of coherence can
be done based on the volume proposal plus chapter abstracts. It would be
very uncommon for an author to completely change the topic of their
contribution between the initial abstract and the final contribution.
When the VE submits the proposal+chapter abstracts to the SE, the SE has
several ways of influencing the coherence:
\begin{itemize}
 \item  accept proposal
 \item  reject proposal
 \item  ask for modification of proposal (less theory-internal, wider coverage)
 \item  ask for clearer focus of chapters to remove overlap
 \item  ask for more focus in selection of chapters, possibly via the removal of certain chapters
\end{itemize}
-

After this step is completed, the authors create the initial versions of
the chapters, which have to undergo the assurance of scientific merit.
This is where things get complicated. The following problems have to be
addressed:

\begin{itemize}
 \item  bad science or unreadable papers should not be published
 \item  the process should not take to long
 \item  there should be ideally only be one round of revisions. Implementing revisions suggested by a reviewer only to be told by an ulterior reviewer that these revisions were unnecessary and should be undone is one of the most frustrating experiences in science.
 \item  reviews should have an impact. Do not ask for reviews if you are going to accept/reject the work anyway.
\end{itemize}

It is typical for edited volumes that papers get reviewed by the other
contributors, who are often also specialists in the very narrow domain the book is about. Nevertheless, appeal to a broader readership is also important. Therefore, the internal review is often complemented by an external reviewer.

There are three ways to assure the scientific merits of the papers in an edited volume. I will call them the "Delegated system", the "Compliance system" and the "Two-reviews-system".

\section*{Delegated review}

In the delegated system, the SE entrusts the VE with the assurance of the scientific merit. This is similar to the role of a guest editor for special issues of journals. The SE values the opinion of the VE and accepts their judgment as to which papers are valuable without further ado. 
\begin{figure}
\begin{tikzpicture}[-latex]
  \matrix (chart)
    [
      matrix of nodes,
      column sep      = 3em,
      row sep         = 5ex,
      column 1/.style = {nodes={treenode}},
      column 2/.style = {nodes={treenode}},
      column 3/.style = {nodes={treenode}},
      column 4/.style = {nodes={treenode}},
      column 5/.style = {nodes={treenode}},
      row 1/.style = {nodes={dummy}}
%       column 2/.style = {nodes={env}}
    ]
    {
      author  & volume editor & reviewer~1 & series editor & reviewer~2\\
			& proposal      &           &               &           \\
			& 		 &           &     review        &           \\
			& accept            &           &               &           \\
	create manuscript 	&               &           &               &           \\
			& collect       &           &               &           \\
			&               &  review       &               &           \\
			& compile change requests & &               &           \\
	revise		&               &           &               &           \\
			&  accept       &           &    receive    &           \\
			&               &            & |[finish]| publish \\
    };
  \draw
    (chart-2-2) \oben{submit\hspace{9mm}} (chart-3-4)
    (chart-3-4) \unten{delegate} (chart-4-2)
    (chart-4-2) \unten{\hspace{3mm}invite} (chart-5-1)
    (chart-5-1) \oben{\hspace{9mm}submit} (chart-6-2)
    (chart-6-2) \oben{\hspace{9mm}forward} (chart-7-3)
    (chart-7-3) \rechts{\hspace{3mm}send} (chart-8-2)
    (chart-8-2) \oben{\parbox{2cm}{request\\ revision}\hspace{13mm}} (chart-9-1)
    (chart-9-1) \rechts{submit~~~~} (chart-10-2)
    (chart-10-2) \oben{submit} (chart-10-4)
    (chart-10-4) edge (chart-11-4); 
\end{tikzpicture} 
\caption{Delegation}
\end{figure}
\newpage

\section*{Volume Review: Compliance review}


In the compliance system, the VE submits all initial papers, the reviews and the revised version to the SE. The SE then sends this collection out for compliance review. Compliance review means that the reviewers should check for whether the established best practices have been adhered to. Has each paper been reviewed? Were the reviewers independent? Are the reviews thorough? Have the reviewers recommendations been followed? The compliance reviewers are not requested to evaluate the scientific merit again. Their task is rather a kind of "meta-evaluation" whether due process was followed. 

\begin{figure}
\begin{tikzpicture}[-latex]
  \matrix (chart)
    [
      matrix of nodes,
      column sep      = 3em,
      row sep         = 5ex,
      column 1/.style = {nodes={treenode}},
      column 2/.style = {nodes={treenode}},
      column 3/.style = {nodes={treenode}},
      column 4/.style = {nodes={treenode}},
      column 5/.style = {nodes={treenode}},
      row 1/.style = {nodes={dummy}}
%       column 2/.style = {nodes={env}}
    ]
    {
      author  & volume editor & reviewer~1 & series editor & reviewer~2\\
			& proposal      &           &               &           \\
			& 		 &           &     review        &           \\
			& accept            &           &               &           \\
	create manuscript 	&               &           &               &           \\
			& collect       &           &               &           \\
			&               &  review       &               &           \\
			& compile change requests & &               &           \\
	revise		&               &           &               &           \\
			&    compile final version    &           &        &           \\
			&    document process		    &           &    receive documentation    &           \\
			&               &           &     	     &  compliance review        \\
			&               &           &    accept    &           \\
			&               &            & |[finish]| publish \\
    };
  \draw
    (chart-2-2) \oben{submit\hspace{9mm}} (chart-3-4)
    (chart-3-4) \unten{invite} (chart-4-2)
    (chart-4-2) \unten{\hspace{3mm}invite} (chart-5-1)
    (chart-5-1) \oben{\hspace{9mm}submit} (chart-6-2)
    (chart-6-2) \oben{\hspace{9mm}forward} (chart-7-3)
    (chart-7-3) \rechts{\hspace{3mm}send} (chart-8-2)
    (chart-8-2) \oben{\parbox{2cm}{request\\ revision}\hspace{13mm}} (chart-9-1)
    (chart-9-1) \rechts{submit~~~~} (chart-10-2)
    (chart-10-2) edge (chart-11-2)
    (chart-11-2) \oben{submit} (chart-11-4)
    (chart-11-4) \oben{\hspace{9mm}forward} (chart-12-5)
    (chart-12-5) \oben{recommend\hspace*{14mm}} (chart-13-4)
    (chart-13-4) edge (chart-14-4); 
\end{tikzpicture} 
\caption{Compliance review}
\end{figure}
\newpage
\section*{Two reviews-systems}
The two review system comes in two kinds. The first kind is the "Early Two Reviews System", the second kind is the "Late Two Reviews System".

\subsection*{Early Two Reviews System}
 In the Early Two Reviews System, the VE submits all initial submissions they wish to include together with the reviews to the SE. The SE then gets reviews for that material and decides whether to accept the submission. The early two review system is similar to the Compliance System in that the reviewer gets to see the first round reviews. If this second-level reviewer recommends acceptance, the SE informs the VE that the first-level reviews can be sent to the authors. The book counts as accepted. The incorporation of the changes by the authors is subsequent to this. The final version of the edited volume is sent to the Series editor and counts as accepted. In that sense, the Early Two Review System is similar to the Delegated System because a rejection is no longer possible at that point in time. 


\subsection*{Late Two Reviews System}
The late two reviews system differs from the Early Two Reviews System in that the version sent to the second tier reviewers is not the initial one, but the one which already incorporates the first-tier reviewers' comments. This will make it easier for the second-level reviewer to judge the papers, but it can also lead to frustration if the book ends up being turned down and the authors' work on revising the papers based on the first-tier comments was for nothing. Second level reviewers in the Late Two Reviews System only judge the global scientific merit of the final volume. A judgment of the procedure is then not necessary.


\begin{figure}
\begin{tikzpicture}[-latex]
  \matrix (chart)
    [
      matrix of nodes,
      column sep      = 3em,
      row sep         = 5ex,
      column 1/.style = {nodes={treenode}},
      column 2/.style = {nodes={treenode}},
      column 3/.style = {nodes={treenode}},
      column 4/.style = {nodes={treenode}},
      column 5/.style = {nodes={treenode}},
      row 1/.style = {nodes={dummy}}
%       column 2/.style = {nodes={env}}
    ]
    {
      author  & volume editor & reviewer~1 & series editor & reviewer~2\\ 
	create manuscript 	&               &           &               &           \\
			& collect       &           &               &           \\
			&               &  review       &               &           \\
			& select papers & &               &           \\
			& compile documentation & &    receive           &           \\ 
			&               &           &     	     &  evaluate content        \\
			&               &           &     	     &  evaluate procedure        \\
			&  compile change requests             &           &    decide    &           \\ 
	revise		&               &           &               &           \\
			&    compile final version    &           &     accept   &           \\ 
			&               &            & |[finish]| publish \\
    };
  \draw 
    (chart-2-1) \oben{\hspace{9mm}submit} (chart-3-2)
    (chart-3-2) \oben{\hspace{9mm}forward} (chart-4-3)
    (chart-4-3) \rechts{\hspace{3mm}send} (chart-5-2) 
    (chart-5-2) edge (chart-6-2) 
    (chart-6-2) \oben{\hspace{3mm}submit} (chart-6-4) 
    (chart-6-4) \rechts{\hspace{3mm}forward} (chart-7-5) 
    (chart-7-5)  edge (chart-8-5) 
    (chart-8-5) \rechts{\hspace{3mm}send} (chart-9-4) 
    (chart-9-4) \oben{\hspace{3mm}forward} (chart-9-2)
    (chart-9-2) \rechts{\hspace{3mm}request revisions} (chart-10-1)
    (chart-10-1) \links{\hspace{3mm}submit} (chart-11-2)
    (chart-11-2) \oben{\hspace{3mm}submit} (chart-11-4) 
    (chart-11-4) edge (chart-12-4) 
;
\end{tikzpicture} 
\caption{Early two review system}
\end{figure}
 

\begin{figure}
\begin{tikzpicture}[-latex]
  \matrix (chart)
    [
      matrix of nodes,
      column sep      = 3em,
      row sep         = 5ex,
      column 1/.style = {nodes={treenode}},
      column 2/.style = {nodes={treenode}},
      column 3/.style = {nodes={treenode}},
      column 4/.style = {nodes={treenode}},
      column 5/.style = {nodes={treenode}},
      row 1/.style = {nodes={dummy}}
%       column 2/.style = {nodes={env}}
    ]
    {
      author  & volume editor & reviewer~1 & series editor & reviewer~2\\ 
	create manuscript 	&               &           &               &           \\
			& collect       &           &               &           \\
			&               &  review       &               &           \\
			& compile change requests & &               &           \\
	revise		&               &           &               &           \\
			&    compile final version    &           &        &           \\
			&    document process		    &           &    receive documentation    &           \\
			&               &           &     	     &  evaluate content        \\ 
			&               &           &    accept    &           \\
			&               &            & |[finish]| publish \\
    };
  \draw 
    (chart-2-1) \oben{\hspace{9mm}submit} (chart-3-2)
    (chart-3-2) \oben{\hspace{9mm}forward} (chart-4-3)
    (chart-4-3) \rechts{\hspace{3mm}send} (chart-5-2)
    (chart-5-2) \oben{\parbox{2cm}{request\\ revision}\hspace{13mm}} (chart-6-1)
    (chart-6-1) \rechts{submit~~~~} (chart-7-2)
    (chart-7-2) edge (chart-8-2)
    (chart-8-2) \oben{submit} (chart-8-4) 
    (chart-8-4) \rechts{forward} (chart-9-5) 
    (chart-9-5) \oben{recommend\hspace*{14mm}} (chart-10-4)
    (chart-10-4) edge (chart-11-4); 
\end{tikzpicture}  
\caption{Late two review system}
\end{figure}

\end{document}